---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cmap

<!-- badges: start -->
[![R-CMD-check](https://github.com/mdsumner/cmap/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mdsumner/cmap/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of cmap is to provide colours from matplotlib. 

## Installation

You can install the development version of cmap like so:

``` r
pak::pkg_install(file.path("mdsumner", "cmap"))
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(cmap)
pal <- cm_pal("gnuplot")
image(volcano, col = pal(100, alpha = 0.5))

par(mfrow = n2mfrow(4))
for (i in 1:4) {
image(volcano, col = cm_pal(nm <- sample(cm_names(), 1))(64), main = nm)
}

```


You can also use the cm object itself, but we haven't thought about that much yet. 


```{r cm-object}
cmap:::cm$brg(seq(0, 1,length.out = 5))

```

## Code of Conduct
  
Please note that the cmap project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
